A Geometry for Network Visualization in \MakeLowercase{\texttt{ggplot2}}

### 2015-04-01 CC/writeup.Rnw
final version (for now)

<<email_ex_facet, fig.height=8, fig.width=8, fig.cap = 'All emails within a company over a two week period facetted by day of the month.',echo=TRUE>>=

@@

\includegraphics[width=\textwidth]{figure/email_ex_facet-1.pdf}

>>>>

<<email_ex_facet, fig.height=8, fig.width=8, fig.cap = 'All emails within a company over a two week period facetted by day of the month.',echo=TRUE,eval=FALSE>>=

@@

\includegraphics[width=8in]{figure/email_ex_facet-1.pdf}
